\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}


\raggedbottom
\raggedright

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]



\begin{document}
\begin{center}
\thispagestyle{empty}
\huge \textbf{Sesha N.S.L Sai Charla \\}
\small Graduate Student $\cdot$ School of Aeronautics and Astronautics $\cdot$ Purdue University\\
\small scharla@purdue.edu $\mid$ +1 (765) 714 4235   \\
%\hrulefill
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OBJECTIVE
% Who you are, what domain, what are you looking for and when?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\noindent \textbf{\underline{OBJECTIVE}} \\
%\noindent Graduate student looking for domain positions starting month and year. \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS: Important and relevant to the job you are applying for
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\noindent \textbf{\underline{CORE SKILLS}} \\
%Skill 1 (years of experience), Skill 2 (years of experience), Skill 3 (years of experience) \\
% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentor and mentees for Android and iOS platform.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{WORK EXPERIENCE} 
\noindent \textbf{Purdue University} \hfill West Lafayette, IN, USA \\
\noindent \textit{Graduate Research Assistant, Flight Dynamics, Controls and Hybrid Systems Lab} \hfill Aug. 2020 $-$ prsent
\begin{itemize}[noitemsep,nolistsep,leftmargin=0.25in,label={--}]
    \item Worked on research problem formulation, quarterly report to funding agency and monthly presentations to the collaborators regarding the project: "Cyber-physical security of Urban Air Mobility (UAM) systems".
    \item Also worked on "Human Machine Mutual Adaptatation Project" alongside the thesis work on "Simplix Chain Design for Reach Control".
\end{itemize}

\vspace{3pt}
\noindent \textit{Graduate Teaching Assistant, AAE 421: Flight Dynamics and Controls by prof. Ran Dai} \hfill Aug. 2020 $-$ Dec 2020
\begin{itemize}[noitemsep,nolistsep,leftmargin=0.25in,label={--}]
    \item Prepared homework and exam solutions, coordinated grading with one another TA and a grader and organized office hours for explaining the concepts to students.
\end{itemize}

\vspace{5pt}
\noindent \textbf{U.R Rao Satellite centre (URSC) - Indian Space Research Organization (ISRO)} \hfill Benguluru, India \\
\textit{Project Manager: Thermal Testin, Human Space Program (HSP)} \hfill Jan. 2019 $-$ Jul. 2019
\begin{itemize}[noitemsep,nolistsep,leftmargin=0.25in,label={--}]
    \item Organized meetings to finalize test procedures and necessary infrastructure for thermal vacuum and thermal balance testing of the proposed designs of the spacecraft.
\end{itemize}

\vspace{3pt}
\textit{Test Engineer [Scientist/Engineer "SC"], Thermal Systems Group} \hfill Jul. 2016 $-$ Jul. 2019
\begin{itemize}[noitemsep,nolistsep,leftmargin=0.25in,label={--}]
    \item Conducted Thermal Vacuum and Thermal Balance tests of $25$ \textbf{satellites} in 3 years as a part of a team of 8 engineers.
	\item \textbf{Led a team} of 4 engineers and 2 technicians for Thermal Vacuum and Thermal Balance tests of \textbf{Chandrayan-2} (the lunar lander project of ISRO) mission's orbitor, lander and rover. 
    \item Augmented the software of existing \textbf{SCADA} systems for simultaneous testing of multiple satellites.  
	\item Started a technology development program: \textbf{Automation of thermal control during Satellite Tests}
	\item Involved in technology development programs: $(1)$ Structural analysis of a \textsc{Passive Radiative Cooler}. $(2)$ DSMC method for Aerobreaking.
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EDUCATION}
\noindent \textbf{Purdue University}, \textit{School of Aeronautics and Astronautics} \hfill West Lafayette, IN, USA \\
\textit{Masters in Aeronautics and Astronautics} \hfill Aug. 2019 $-$ May. 2021 (Anticipated)\\
\textsc{Major}: Controls and Autonomy, \textsc{Minor}: Machine Learning \hfill \textsc{Adviser}: Prof. Inseok Hwang\\
\textsc{Course Work}: AAE 668: Hybrid Systems, ME 677: Non-linear Systems, AAE 564: Linear Systems,  AAE 568: Optimal Control, ECE 680: Modern Automatic Control, CS 590: Reinforcemant Learning, ECE 595: Machine Learning 1, STAT 545: Computational Statistics
\hfill \textsc{GPA}: $3.84/4$\\
\textsc{Theis Title}: Simplex Chain Design for Reach Control \\

\vspace{5pt}
\noindent \textbf{Indian Institute of Science}, \textit{Center for Continuing Education} \hfill Jan. 2017 $-$ May. 2018  \hfill Bengaluru, India \\
\textsc{Course Work:} Embedded Systems on ARM, Structural Optimization and Vibration and Noise Control \\

\vspace{5pt}
\noindent \textbf{Indian Institute of Space Science and Technology (IIST)} \hfill Thiruvananthapuram, India\\
\textit{Bachelor of Technology in Aerospace Engineering} \hfill \textsc{GPA}: $8.34/10$ \hfill Aug. 2012 $-$ May. 2016 \\
\textsc{Theis Title}: Modelling and Simulation of a Flexible Launch Vehicle
\hfill \textsc{Adviser}:Prof. K. Kurien Issac \\
\textsc{Major Projects}: $(1)$ Control of an Under-Actuated System: Torque Limited Pendulum \hfill {Summer 2015}\\
$(2)$ Design and Development of a Flapping Wing Micro Air Vehicle \hfill {Nov. 2013 $-$ Dec. 2014}\\
Receipient of \textit{DOS-ISRO Scholarship}.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Technical Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{TECHNICAL SKILLS}
\begin{tabular}{l c l}
	\textsc{Programming Languages}&:& Python, Bash, R, MATLAB,C, C++ \\
	\textsc{OS \& Software Tools}&:& Linux, Git, vim, \LaTeX, MS Office\\
    \textsc{Drafting and CAD Tools}&:& AutoCad, Catia, Solid Works, NX\\
    \textsc{Development Boards}&:& ARM Cortex M3/M4 (TM4C123GXL), Arduino, Raspberry PI\\
	\textsc{Manufacturing}&:& Machining - Lathe, Milling, Drilling, Grinding,
	Welding\\
\end{tabular}
\end{document}
