\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}
%\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\raggedbottom
\raggedright

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}\titlerule \vspace{-5pt}]


\begin{document}
\begin{center}
\thispagestyle{empty}
\huge{\textit{Sesha N.} \textsc{Charla}}\\
\small PhD Student $\cdot$ School of Mechanical Engineering $\cdot$ Purdue University\\
\small scharla@purdue.edu $\mid$ +1 (765) 714 4235   \\
\end{center}


\begin{tabular}{l c l}
    {\large{\textsc{Objective}}}&:& Graduate Research Assistantship\\
{\large{\textsc{Core Skills}}}&:& Control Theory, Dynamic Modelling, Estimation,
System Identification and Optimization.\\
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Work Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
\noindent \textsc{SC Solutions} \hfill Portlabd, Oregon, USA.\\
\vspace{3pt}
\textbf{\textit{Research Engineer (Intern)}} \hfill May. 2023 $-$ Aug. 2023
\begin{itemize}[noitemsep,nolistsep,leftmargin=0.25in,label={--}]
    \item Developing computer vision deployment pipeline and estimation algorithms for parameter estimation using vision data.
    \item Deploying realtime control systems using windows real-time extension.
\end{itemize}
%===============================================================================
%===============================================================================
\vspace{10pt}
\noindent \textsc{Virgin Hyperloop} \hfill Los Angeles, California, USA.\\
\vspace{3pt}
\textbf{\textit{Motion Control Engineer (Intern)}} \hfill Jun. 2022 $-$ Aug. 2022
\begin{itemize}[noitemsep,nolistsep,leftmargin=0.25in,label={--}]
    \item Developed a supervisory control for minimizing the force mismatch
across the bogie for improving EM engine efficiency and worked out the necessary
requirements through cross team meetings.
\item Refined the control architecture for single EM engine control and
demonstrated the limitation of the linear design on the non-linear system.
\item Developed a MIMO model for the guidance bogie engine assembly and worked
out the stability of off-diagonal elements w.r.t suspension parameters.
\end{itemize}
%===============================================================================
%===============================================================================
\vspace{10pt}
\noindent \textsc{U.R Rao Satellite centre (URSC) - Indian Space Research
Organization (ISRO)} \hfill Bengaluru, India \\
\vspace{3pt}
\textbf{\textit{Thermal Test Engineer, Thermal Systems Group}} \hfill Jul. 2016 $-$ Jul. 2019
\begin{itemize}[noitemsep,nolistsep,leftmargin=0.25in,label={--}]
    \item Worked thermal instrumentation and control for thermal-vacuum and thermal-balance tests of satellite systems.
	\item Team lead for \textit{Chandrayan-2} (the lunar lander project of ISRO) mission's orbiter, lander and rover.
    \item Augmented the software of existing \textit{SCADA} system for simultaneous testing of multiple satellites, doubling the productivity of test systems.
	\item Improved and standardized the heater design through a web application to streamline PI gain tuning and in-situ heater sensor mapping.
    \item Held the position of \textit{Project Manager, Thermal Testing, Human Space Program (HSP)} from Jan. $2019$ to Jul. $2019$, to assist in development of procedures and infrastructure for thermal vacuum and thermal balance testing of the proposed new designs of the spacecrafts.\\
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PUBLICATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand\refname{Publications}
\nocite{improvBandwidth}
\bibliographystyle{unsrt}
\bibliography{ref}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\noindent \textsc{Purdue University}, \textit{School of Mechanical Engineering} \hfill West Lafayette, IN, USA \\
\textbf{\textit{PhD in Mechanical Engineering}} \hfill Aug. 2021 $-$ Present\\
\textsc{Area}: \textit{\textbf{Systems, Measurement and Controls}}  \hfill \textsc{Advisor}: Prof. Bin Yao\\
\textsc{Course Work:} ME 586: Microprocessors in Electromechanical Systems, ME
584: System Identification, ME 675: Multivariable Control, ME 565: Vehicle Dynamic and Controls, MA 543: Ordinary Differential Equations
\textsc{Thesis Project}: Fault-tolerant controller design and implementation for a fully actuated tilted-wing hexrotor for aerial manipulation.\hfill \textsc{GPA}: $3.75/4$\\
\vspace{5pt}
\noindent \textsc{Purdue University}, \textit{School of Aeronautics and Astronautics} \hfill West Lafayette, IN, USA \\
\textbf{\textit{Masters in Aeronautics and Astronautics}} \hfill Aug. 2019 $-$ Aug. 2021\\
\textsc{Major}: \textit{\textbf{Autonomy and Controls}}, \textsc{Minor}: \textit{\textbf{Machine Learning}}
\hfill Advisor: Prof. Inseok Hwang\\
\textsc{Course Work}: ME 686: Adaptive Control, AAE 668: Hybrid Systems, ME 677: Non-linear Systems, AAE 564: Linear Systems,  AAE 568: Optimal Control, ECE 680: Modern Automatic Control, CS 590: Reinforcement Learning, ECE 595: Machine Learning 1, STAT 545: Computational Statistics, MA 514 : Numerical Analysis
\hfill \textsc{GPA}: $3.78/4$\\

\vspace{5pt}
\noindent \textsc{Indian Institute of Space Science and Technology (IIST)} \hfill Thiruvananthapuram, India\\
\textbf{\textit{Bachelor of Technology in Aerospace Engineering}} \hfill \textsc{GPA}: $8.34/10$ \hfill Aug. 2012 $-$ May. 2016 \\
\textsc{Thesis}: Finite Element Dynamic Model using Lagrangian for Launch
Vehicle Bending and Trajectory Simulations.
Recipient of \textit{DOS-ISRO Scholarship}.
\hfill \textsc{Adviser}: Prof. K. Kurien Issac \\

%===============================================================================
% Academic Work Experience
%===============================================================================
\section{Academic Work Experience}
\noindent \textsc{Purdue University} \hfill West Lafayette, IN, USA \\
\vspace{3pt}
\noindent \textbf{\textit{Graduate Teaching Assistant}} \hfill Aug. 2020 $-$ Present\\
\begin{itemize}[noitemsep,nolistsep,leftmargin=0.25in,label={--}]
\item Teaching Assistant for graduate laboratory courses on Mechatronics (ME 588) and Microprocessors and Electromechanical Systems (ME
586) and undergraduate laboratory courses in Measurement and Control (ME 375, ME 365, AAE 364, AAE 421).
\item The laboratory courses involve assiting students in writing C, Assembly and LabView programs, and debugging.
\item Developed and demonstrated control implementation procedures for refrigeration system with variable speed compressor and flow control valve using STM32 Discovery board as possible guided final project for the future course offerings of ME 586.
\end{itemize}
\vspace{3pt}
\noindent \textbf{\textit{Graduate Research Assistant (Masters)}} \hfill Aug. 2020 $-$ May. 2021\\
\textit{Flight Dynamics, Controls and Hybrid Systems Lab}
\begin{itemize}[noitemsep,nolistsep,leftmargin=0.25in,label={--}]
	\item Developed a simplex chain design methodology using convex optimization for solving control problems specified using linear temporal logic (Reach Control Problem) in up to 3-dimensional state spaces with multiple control inputs and explored its possible applications to shared control and path planning.
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Technical Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Skills}
(years of experience)
\begin{tabular}{l c l}
    \textsc{Control Engineering} ($7+$ years) &:& Robust control, MIMO systems, Adaptive and Nonlinear control, \\
    & & Optimal Control and Estimation, and System Identification\\
	\textsc{Programming Languages}&:& Python($10+$), MATLAB ($10+$), C($5$), C++($3$), Bash($5$), R($<1$), Julia($<1$)\\
    \textsc{Embedded Programming}&:& C($2+$), C++($1+$), ARM Cortex-M3/M4 Assembly ($2$), \\ & &LabView for NI-MyRio ($3+$)\\
	\textsc{OS \& Software Tools}&:& Linux($10+$), Git($10+$), Simulink($10+$), Jira, \LaTeX ($10+$)\\
	\textsc{Machining} (3 years) &:& Lathe, Milling, Drilling; CNC programming\\
\end{tabular}
\end{document}
